Tight Generalization Bounds for Hard Parameter Sharing in High-dimensional Linear Regression

### 2020-10-04 arxiv/diff_cov.tex
section 5 wip

The different covariates setting differs from the same covariates setting in two key aspects.
First, different tasks may have different sample sizes. In extreme scenarios, one task may have much less labeled data compared to another task.
Second, the features of different tasks may have different shapes, a phenomenon that is often called ``covariate shift''.
In this section, we show how to deal with the the above two aspects.

When the covariates across tasks are different, we can no longer obtain an optimal solution for minimizing equation \eqref{eq_mtl} as in Claim \ref{lem_exp_opt}.
This is because the minimization problem is non-convex with respect to $A$ and $B$.
Therefore, we consider an arbitrary local minimum of equation \eqref{eq_mtl} and provide generalization bounds that scale with key properties of task data.
We focus on the two-task case to better understand the impact of having different sample sizes and different covariates in hard parameter sharing.

@@

\begin{corollary}\label{cor_MTL_loss}
	In the setting of Example \ref{ex_sample_ratio}, assume that
	%a) the sample sizes $n_1$ and $n_2$ are greater than $(1 + \tau) p$, b) $\Sigma_1=\Sigma_2=\id_p$, and c) %there exists a small constant $c_0>0$ such that
	(i) task one's sample size is at least $n_1 \ge \min(\frac{17}{\varepsilon^2}, 50) \cdot p$ for a fixed positive value $\varepsilon$, and task two's sample size is at least $n_2 \ge \frac{3}{2}p$;
	(ii) the noise variance is smaller than the signal strength: $\sigma^2 \lesssim  \kappa^2$;
%	\be\label{choiceofpara0}
%	p^{-1/2+c_0}\sigma^2 + p^{c_0}d^2\le \kappa^2\le p^{1-c_0} (\sigma^2 +d^2)  .  	\ee
	%\be\label{choiceofpara0}
%	(ii) the task-specific variance of $\beta_i$ is much smaller than the signal strength {\color{red}$d^2 = \oo( {\kappa^2})$}; \HZ{what does $\ll$ mean exactly?}
%	(iii) the sample sizes $n_1$ and $n_2$ are greater than $(1 + \tau) p$.
	(iii) the task-specific variance of $\beta_i$ is much smaller than the shared signal strength: $d^2 \le p^{-c_{\varphi}}{\kappa^2}$.
	The prediction loss of hard parameter sharing for task two satisfies that
	\begin{align}\label{cor_MTL_error}
	%-\left[1- \left( 1-\frac{1}{\sqrt{\rho_1}}\right)^4\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2)  \le
	  \left|L(\hat{\beta}_2^{\MTL}) - \frac{d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} -\frac{\sigma^2 p}{n_1 + n_2 - p}  \right| \le \varepsilon \cdot \frac{d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} + p^{-c_{\varphi}} \cdot \OO(d^2 + \sigma^2).
	%\left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] d^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \\
	%& +C \left[(p^{-c_\varphi}+p^{-c_\infty/2})(\sigma^2 +d^2)+p^{-c_\infty}\kappa^2 + %\frac{d^4+\sigma^2 d^2}{\kappa^2}\right],\nonumber
	 \end{align}
%	 for a large constant $C>0$.
\end{corollary}

@@

Our result shows that the prediction loss of hard parameter sharing consists of a bias term that scales with task-specific variance $d^2$ and a noise variance term that scales with $\sigma^2$.
In the following, we explain an interesting phenomenon, where adding task one's samples helps task two initially, but hurts eventually.
Consider the prediction loss if we fix $n_2$ and increase $n_1$.
First, the noise variance term in Corollary \ref{cor_MTL_loss} always reduces as $n_1$ increases.
Second, the bias term always increases as $n_1$ increases, which can be verified by calculating the derivative of the bias term.
Combined together, we observe that the \textit{optimal} sample ratio between $n_1$ and $n_2$ should be among one of following three cases:
(i) $n_1 = 0$, in which case the prediction loss reduces to $\frac{\sigma^2 p}{n_2 - p}$;
(ii) $n_1 = \infty$, in which case the prediction loss reduces to $d^2$;
(iii) the critial point where the derivative of the bias and the variance terms w.r.t. $n_1$ equals zero.

@@

As a remark, by combining the bias and variance asymptotics, we can obtain the generalization error of hard parameter sharing for any local minimum solutions $(A, B)$.
Since the proof is similar to the same covariates setting and Example \ref{cor_MTL_loss}, we describe the main differences and omit the rest of the details.
First, we will rescale $X_1$ by $A_1 / A_2$ before applying Theorem \ref{thm_main_RMT}.
Second, we approximate ${X^{(1)}}^{\top}X^{(1)}$ by $n_1 \Sigma^{(1)}$ in equation \eqref{eq_diff_cov} using Fact \ref{lem_minv}.
For the rest of this section, we present the main ideas in the proof of Theorem \ref{thm_main_RMT}.
The full proof can be found in Section \ref{sec_maintools}.
%Proposition \ref{prop_covariate} implies that when $\rho_1\gg \rho_2$, having no covariate shift is the optimal choice for choosing the source task.
%This provides evidence that covariate shift is unfavorable when there are many source task datapoints,

%\todo{} To complement the result, we show an example when the statement is not true if $n_1 \le n_2$.

>>>>

The different covariates setting differs from the same covariates setting in two key aspects.
First, different tasks may have different sample sizes. In extreme scenarios, one task may have much less labeled data compared to another task.
Second, the features of different tasks may have different shapes, a phenomenon that is often called ``covariate shift''.
In this section, we show how to deal with these two aspects.

Unlike the previous section, we no longer have an optimal solution for $A$.
This is because the minimization problem is non-convex with respect to $A$ and $B$.
Therefore, we consider an arbitrary local minimum of equation \eqref{eq_mtl} and provide generalization bounds that scale with key properties of task data.
We focus on the two-task case to better understand the impact of having different sample sizes and different covariates in hard parameter sharing.

@@

\begin{corollary}\label{cor_MTL_loss}
	In the setting of Example \ref{ex_sample_ratio}, assume that
	%a) the sample sizes $n_1$ and $n_2$ are greater than $(1 + \tau) p$, b) $\Sigma_1=\Sigma_2=\id_p$, and c) %there exists a small constant $c_0>0$ such that
	(i) task one's sample size is at least $n_1 \ge \min(\frac{17}{\varepsilon^2}, 50) \cdot p$ for a fixed positive value $\varepsilon$, and task two's sample size is at least $n_2 \ge \frac{3}{2}p$;
	(ii) the noise variance is smaller than the signal strength: $\sigma^2 \lesssim  \kappa^2$;
%	\be\label{choiceofpara0}
%	p^{-1/2+c_0}\sigma^2 + p^{c_0}d^2\le \kappa^2\le p^{1-c_0} (\sigma^2 +d^2)  .  	\ee
	%\be\label{choiceofpara0}
%	(ii) the task-specific variance of $\beta_i$ is much smaller than the signal strength {\color{red}$d^2 = \oo( {\kappa^2})$}; \HZ{what does $\ll$ mean exactly?}
%	(iii) the sample sizes $n_1$ and $n_2$ are greater than $(1 + \tau) p$.
	(iii) the task-specific variance of $\beta_i$ is much smaller than the shared signal strength: $d^2 \le p^{-c_{\varphi}}{\kappa^2}$.
	The prediction loss of hard parameter sharing for task two satisfies that
	\begin{align}\label{cor_MTL_error}
	%-\left[1- \left( 1-\frac{1}{\sqrt{\rho_1}}\right)^4\right] pd^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} +\OO(p^{-c}\sigma^2)  \le
	  \left|L(\hat{\beta}_2^{\MTL}) - \frac{d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} -\frac{\sigma^2 p}{n_1 + n_2 - p}  \right| \le \varepsilon \cdot \frac{d^2 n_1^2 (n_1 + n_2)}{(n_1 + n_2 - p)^3} + p^{-c_{\varphi}} \cdot \OO(d^2 + \sigma^2) +{\color{red} p^{-c_\infty}\cdot \OO(\kappa^2)}.
	%\left[\left( 1+\frac{1}{\sqrt{\rho_1}}\right)^4-1\right] d^2\cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \\
	%& +C \left[(p^{-c_\varphi}+p^{-c_\infty/2})(\sigma^2 +d^2)+p^{-c_\infty}\kappa^2 + %\frac{d^4+\sigma^2 d^2}{\kappa^2}\right],\nonumber
	 \end{align}
	 {\color{red}[FY: there is an extra $\kappa^2$ term]}
%	 for a large constant $C>0$.
\end{corollary}

@@

Our result shows that the prediction loss of hard parameter sharing consists of a bias term that scales with task-specific variance $d^2$ and a noise variance term that scales with $\sigma^2$.
In the following, we explain an interesting phenomenon, where adding task one's samples helps task two initially, but hurts eventually.
Consider the prediction loss if we fix $n_2$ and increase $n_1$.
First, the noise variance term in Corollary \ref{cor_MTL_loss} always reduces as $n_1$ increases.
Second, the bias term always increases as $n_1$ increases, which can be verified by calculating the derivative of the bias term.
Combined together, we observe that the \textit{optimal} sample ratio between $n_1$ and $n_2$ should be among one of following three cases:
(i) $n_1 = 0$, in which case the prediction loss reduces to $\frac{\sigma^2 p}{n_2 - p}$;
(ii) $n_1 = \infty$, in which case the prediction loss reduces to $d^2$;
(iii) the critial point where the derivative of the bias and the variance terms w.r.t. $n_1$ equals zero.
The proof can be found in Appendix \ref{app_iso_cov}.

@@

As a remark, by combining the bias and variance asymptotics, we can also obtain a generalization bound for any local minimum solutions $(A, B)$.
The proof is similar to Theorem \ref{thm_many_tasks} and Corollary \ref{cor_MTL_loss}.
We describe the differences and omit the details.
First, we rescale $X_1$ (and $\Sigma^{(1)}$) by $A_1 / A_2$ before applying Theorem \ref{thm_main_RMT}.
Second, we approximate sample covariance ${X^{(1)}}^{\top}X^{(1)} / n_1$ by its expectation $\Sigma^{(1)}$ in equation \eqref{eq_diff_cov} using Fact \ref{lem_minv}.
For the rest of this section, we present the main ideas for proving Theorem \ref{thm_main_RMT}.
%Proposition \ref{prop_covariate} implies that when $\rho_1\gg \rho_2$, having no covariate shift is the optimal choice for choosing the source task.
%This provides evidence that covariate shift is unfavorable when there are many source task datapoints,

### 2020-10-04 arxiv/experiments.tex
section 5 wip

\subsection{Experimental Setup}

We consider a text classification task and an image classification task as follows.

@@

{\it ChestX-ray14.} This dataset contains 112,120 frontal-view X-ray images \cite{chexnet17}.
There are 14 diseases (tasks) for every image that we would like to predict.
We use densenet121 as the shared module \cite{huang2017densely}.
%We treat each label as one task a binary classification problem and formulate it as a 14-task multi-task learning problem.
%This dataset is curated where the labels
%We use the CheXNet model from~\cite{chexnet}, which is a 121-layer convolutional neural network on all tasks.

\paragraph{Synthetic Settings}\label{app_synthetic}
	We describe the parameter settings used in the synthetic experiments (Figure \ref{fig_model_shift_phasetrans}).
	For all three synthetic experiments, we set the input feature dimension as $p = 200$.
	\squishlist
		\item Task similarity: We use $\rho_1 = 90, \rho_2 = 30$ for sample sizes.
	The noise level is $\sigma = 5$.
	We set $\kappa = 1$ and vary model distance $d$ from $0.01$ to $0.2$.
	The $x$-axis measures the function $\Phi(\beta_1, \beta_2)$ described in Section \ref{sec_similarity}.
	The $y$-axis measures the improvement of prediction loss using MTL compared to STL.
		\item Sample size: We set $\kappa = 1$ and $d = 0.02$ for model distance.
	We use $\rho_2 = 500$ and vary $\rho_1$ from $50$ to $800$ for sample sizes.
		\item Covariate shift: We set $\kappa = 1$ and $d = 0$.
	We set $\rho_2 = 4$ and vary $\rho_1$ from $5$ to $25$ for sample sizes.
	We use the scale parameter $\lambda = 1$ for the curve without covariate shift and $\lambda = 2$ for the curve with covariate shift (cf. Section \ref{sec_covshift}).
	Without loss of generality, we have rescaled the $x$ and $y$ axis for the ease of presentation.
	This can be achieved similarly by rescaling the task data.
	\squishend

\paragraph{Image and Text Classification Settings}\label{app_it}

@@

\textit{Predicting transfer effect via STL results.}
We simplify the setup of this experiment by fixing the sample sizes of every task pair.
For sentiment analysis tasks, the sample size of the source task ranges in $500, 1000, 1500$.
We randomly sample these many data points from the task.
The sample size of the target task is $1000$.
For image classification tasks, the training sample size is $10,000$ for every task.

\textit{Mitigating negative transfer via incremental training.}
For the case of two tasks, we compare the incremental training scheduled described in Algorithm \ref{alg_inc_train}  to a round-robin training schedule baseline.
We add $20\%$ of source task samples for every $T = 2$ epochs.
The total number of epochs is $20$.
We set the threshold $\tau$ as the validation accuracy of the target task using the baseline training schedule.

@@

\textit{Validating the Theoretical Results.}
We fill in the details of the experimental procedure used for the results in Figure \ref{fig_ablation}.
\squishlist
	\item Task similarity: We select a similar and a dissimilar source task compared to the target task using domain knowledge.
First pair: the customer review dataset (CR) , which predicts whether a review is positive or negative, is more similar to SST (sentiment treebank) than MPQA (question type).
Second pair: SST is more similar to MR since they both concern about positive or negative opinions expressed the text.
TREC is less similar to MR because the task is about question types.
Third pair: MPQA (opinion polarity) is more similar to TREC (question type)
	\item Sample size: We vary the sample size of the source task from $100$ to $3000$.
	\item Covariate shift: We implement the covariance alignment procedure following \cite{WZR20}.
	We fix the sample size of the target task as $1000$.
\squishend

%\subsection{Validating the Theoretical Results}\label{sec_exp_ab}
%We first validate our theoretical results in Section \ref{sec_similarity} and \ref{sec_data_size}.
%In Figure \ref{fig_ab_sim}, we compare the performance training with a semantically similar task versus a dissimilar task with a target task.
%We select each task pair based on our domain knowledge.
%We observe that adding a similar task helps the target task whereas adding a dissimilar task hurts.
%The rest of experimental procedures are left to Appendix \ref{app_it}.

\subsection{The Same Covariates Setting: Sample Efficiency}

%We validate that MTL performs better when the source task is more similar to the target task.
%We show the result on the sentiment analysis tasks.
%For a target task, we manually select a similar task and a dissimilar task based on prior knowledge.
%Figure \ref{fig_ab_sim} confirms the result.
%Recall that Section \ref{sec_data_size} shows that increasing the data size of the source task does not always improve the performance of MTL for the target task.
%In Figure \ref{fig_ab_data}, we show that for source task MR and target task SST, there is a transition from positive to negative transfer as we increase the data size of the source task.
%Our result provides a fine-grained insight on the covariance alignment algorithm proposed in \cite{WZR20}.
%Recall that the covariance alignment procedure in \cite{WZR20} adds an additional module between the word embedding representation and the shared module.
%When the source task data size is particularly large compared to the target task, we show that applying the covariance alignment algorithm results in more significant gains.
%In Figure \ref{fig_ab_cov}, we observe that the benefit from aligning task covariances becomes more significant for LSTM and MLP as we increase the number of datapoints of the source task.

\begin{table}
	\begin{center}
		\begin{tabular}{c c c c c}
			\toprule
			\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}
				                                                                          MR, SST, SUBJ, CR, MPQA, TREC\end{center}\end{minipage}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}MR, SST, SUBJ, CR, MPQA\end{center}\end{minipage}} \\
			\cmidrule(lr){2-3} \cmidrule(lr){4-5}
			& {\bf Stanford} & {\bf Alignment} & {\bf Stanford} & {\bf Alignment} \\
			\midrule
			{\bf MLP}  & > 100\% & 39\% & 25\% & 25\% \\
			{\bf LSTM} & 36\% & 36\% & 28\% & 25\% \\
			% {\bf CNN}  & 76\% & - & 32\% & -\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Taskonomy experiment.}
	\label{tab:taskonomy}
\end{table}

\begin{figure}[!t]
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=0.98\textwidth]{figures/datapoints_phase_transition.pdf}
		\caption{Sample imbalance}
		\label{fig_size}
	\end{subfigure}\hfill
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=0.98\textwidth]{figures/complementary.pdf}
		\caption{Covariate shift}
		\label{fig_covariate}
	\end{subfigure}\hfill
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=0.98\textwidth]{figures/model_shift_phase_transition.pdf}
		\caption{Sample efficiency}
		\label{fig_model_shift}
	\end{subfigure}
	\caption{%Three takeaways of our theory in Section \ref{sec_insight}.
	We observe a transition from positive to negative transfer as (a) \textit{task model distance} increases and (b) source/target \textit{sample ratio} increases.
	For the special case of having the same task model, we observe in (c) that as source/target \textit{sample ratio} increases, having \textit{covariate shift} worsens the performance of MTL.
	The $y$-axis measures the loss of STL minus MTL.}
	\label{fig_model_shift_phasetrans}
\end{figure}

\subsection{The Different Covariates Setting: Sample Imbalance and Covariate Shift}\label{sec_exp_sample}

In Figure \ref{fig_ab_data}, we validate that adding more source samples does not always improve performance on the target task.
Finally, we validate the algorithmic consequence of Section \ref{sec_covshift}.

\textit{Mitigating negative transfer via incremental training.}
\noindent\textit{Mitigating negative transfer.}
An interesting consequence of Proposition \ref{prop_data_size} is that $L(\hat{\beta}_t^{\MTL})$ is not monotone in $\rho_1$.
In particular, Figure \ref{fig_size} (and our analysis) shows that $L(\hat{\beta}_t^{\MTL})$ behaves as a quadratic function over $\rho_1$.
More generally, depending on how large $\Psi(\beta_1, \beta_2)$ is, $L(\hat{\beta}_t^{\MTL})$ may also be monotonically increasing or decreasing.
Based on this insight, we propose an incremental optimization schedule to improve MTL training efficiency.
\squishlist
	\item We divide the source task data into $S$ batches.
	For $S$ rounds, we incrementally add the source task data by adding one batch at a time.
	\item After training $T$ epochs, if the validation accuracy becomes worse than the previous round's result, we terminate.
	Algorithm \ref{alg_inc_train} in Appendix \ref{app_experiments} describes the procedure in detail.
\squishend

@@

\noindent\textit{Covariance alignemnt.}
Our observation highlights the need to correct covariate shift when $n_1 / n_2$ is large.
Hence for such settings, we expect procedures that aim at correcting covariate shift to provide more significant gains.
We consider a covariance alignment procedure proposed in \cite{WZR20}, which is designed for the purpose of correcting covariate shift.
The idea is to add an alignment module between the input and the shared module $B$.
This new module is then trained together with $B$ and the output layers.
We validate our insight on this procedure in the experiments.

@@

\textbf{Further results of the covariance alignment procedure.}
Our results in Figure \ref{fig_ab_cov} are averaged over all the task pairs.
In Figure \ref{fig_covariate_app}, we show two task pairs as examples.
In Figure \ref{fig_cov_a}, we observe that for the particular task pair, covariance alignment provides more significant gains when the sample ratio is large.
In Figure \ref{fig_cov_b}, we observe that covariance alignment does not always improve over the baseline multi-task learning model.
One explanation is that MR and SST are similar tasks, hence adding the alignment module is unnecessary.
An interesting question is to understand when adding the alignment module benefits the multi-task learning model.
We leave this question for future work.
%Note: For text classification tasks, the source task training data size ranges from 500 to 1,500 and target task training data size is 1000; For ChestX-ray14,

\begin{figure}[!h]
	\centering
	\begin{subfigure}[b]{0.48\textwidth}
		\centering
		\includegraphics[width=0.7\textwidth]{figures/ratio_alignment_norm_trec_cr_lstm.pdf}
		\caption{Task pair TREC and CR}
		\label{fig_cov_a}
	\end{subfigure}\hfill
		\begin{subfigure}[b]{0.48\textwidth}
		\centering
		\includegraphics[width=0.7\textwidth]{figures/ratio_alignment_mr_sst_lstm.pdf}
		\caption{Task pair MR and SST}
			\label{fig_cov_b}
	\end{subfigure}
	\caption{(a) For the task pair TREC and CR, adding the covariance alignment procedure provides more improvement when the source/target sample ratio is large.
	(b) For the task pair MR and SST, adding the covariance alignment procedure hurts performance.
	One explanation is that MR and SST are similar tasks, hence adding the alignment module is unnecessary.}
	\label{fig_covariate_app}
\end{figure}

>>>>

\subsection{Simulation Studies}\label{sec_simulation}

	We describe the parameter settings used in the synthetic experiments (Figure \ref{fig_model_shift_phasetrans}).
	For all three synthetic experiments, we set the input feature dimension as $p = 200$.
	\begin{itemize}
		\item Task similarity: We use $\rho_1 = 90, \rho_2 = 30$ for sample sizes.
	The noise level is $\sigma = 5$.
	We set $\kappa = 1$ and vary model distance $d$ from $0.01$ to $0.2$.
	The $x$-axis measures the function $\Phi(\beta_1, \beta_2)$ described in Section \ref{sec_similarity}.
	The $y$-axis measures the improvement of prediction loss using MTL compared to STL.
		\item Sample size: We set $\kappa = 1$ and $d = 0.02$ for model distance.
	We use $\rho_2 = 500$ and vary $\rho_1$ from $50$ to $800$ for sample sizes.
		\item Covariate shift: We set $\kappa = 1$ and $d = 0$.
	We set $\rho_2 = 4$ and vary $\rho_1$ from $5$ to $25$ for sample sizes.
	We use the scale parameter $\lambda = 1$ for the curve without covariate shift and $\lambda = 2$ for the curve with covariate shift (cf. Section \ref{sec_covshift}).
	Without loss of generality, we have rescaled the $x$ and $y$ axis for the ease of presentation.
	This can be achieved similarly by rescaling the task data.
	\end{itemize}

%Recall that Section \ref{sec_data_size} shows that increasing the data size of the source task does not always improve the performance of MTL for the target task.
%In Figure \ref{fig_ab_data}, we show that for source task MR and target task SST, there is a transition from positive to negative transfer as we increase the data size of the source task.
%Our result provides a fine-grained insight on the covariance alignment algorithm proposed in \cite{WZR20}.
%Recall that the covariance alignment procedure in \cite{WZR20} adds an additional module between the word embedding representation and the shared module.
%When the source task data size is particularly large compared to the target task, we show that applying the covariance alignment algorithm results in more significant gains.
%In Figure \ref{fig_ab_cov}, we observe that the benefit from aligning task covariances becomes more significant for LSTM and MLP as we increase the number of datapoints of the source task.

%\begin{table}
%	\begin{center}
%		\begin{tabular}{c c c c c}
%			\toprule
%			\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}
%				                                                                          MR, SST, SUBJ, CR, MPQA, TREC\end{center}\end{minipage}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}MR, SST, SUBJ, CR, MPQA\end{center}\end{minipage}} \\
%			\cmidrule(lr){2-3} \cmidrule(lr){4-5}
%			& {\bf Stanford} & {\bf Alignment} & {\bf Stanford} & {\bf Alignment} \\
%			\midrule
%			{\bf MLP}  & > 100\% & 39\% & 25\% & 25\% \\
%			{\bf LSTM} & 36\% & 36\% & 28\% & 25\% \\
			% {\bf CNN}  & 76\% & - & 32\% & -\\
%			\bottomrule
%		\end{tabular}
%	\end{center}
%	\caption{Taskonomy experiment.}
%	\label{tab:taskonomy}
%\end{table}

\begin{figure}[!t]
		\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=0.98\textwidth]{figures/model_shift_phase_transition.pdf}
		\caption{Sample efficiency}
		\label{fig_model_shift}
	\end{subfigure}\hfill
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=0.98\textwidth]{figures/datapoints_phase_transition.pdf}
		\caption{Sample ratio}
		\label{fig_size}
	\end{subfigure}\hfill
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=0.98\textwidth]{figures/complementary.pdf}
		\caption{Covariate shift}
		\label{fig_covariate}
	\end{subfigure}
	\caption{%Three takeaways of our theory in Section \ref{sec_insight}.
	We observe a transition from positive to negative transfer as (a) \textit{task model distance} increases and (b) source/target \textit{sample ratio} increases.
	For the special case of having the same task model, we observe in (c) that as source/target \textit{sample ratio} increases, having \textit{covariate shift} worsens the performance of MTL.
	The $y$-axis measures the loss of STL minus MTL.}
	\label{fig_model_shift_phasetrans}
\end{figure}

\subsection{Further Studies on a Text Classification Task}\label{sec_text}

We consider a text classification task as follows.

@@

%{\it ChestX-ray14.} This dataset contains 112,120 frontal-view X-ray images \cite{chexnet17}.
%There are 14 diseases (tasks) for every image that we would like to predict.
%We use densenet121 as the shared module \cite{huang2017densely}.
%We treat each label as one task a binary classification problem and formulate it as a 14-task multi-task learning problem.
%This dataset is curated where the labels
%We use the CheXNet model from~\cite{chexnet}, which is a 121-layer convolutional neural network on all tasks.

%\paragraph{Image and Text Classification Settings}\label{app_it}

@@

\paragraph{Sample ratio.}
In Figure \ref{fig_ab_data}, we validate that adding more source samples does not always improve performance on the target task.
Sample size: We vary the sample size of the source task from $100$ to $3000$.

\textit{Towards computing the optimal sample ratio.}
An interesting consequence of Proposition \ref{prop_data_size} is that $L(\hat{\beta}_t^{\MTL})$ is not monotone in $\rho_1$.
In particular, Figure \ref{fig_size} (and our analysis) shows that $L(\hat{\beta}_t^{\MTL})$ behaves as a quadratic function over $\rho_1$.
More generally, depending on how large $\Psi(\beta_1, \beta_2)$ is, $L(\hat{\beta}_t^{\MTL})$ may also be monotonically increasing or decreasing.
Based on this insight, we propose an incremental optimization schedule to improve MTL training efficiency.
\squishlist
	\item We divide the source task data into $S$ batches.
	For $S$ rounds, we incrementally add the source task data by adding one batch at a time.
	\item After training $T$ epochs, if the validation accuracy becomes worse than the previous round's result, we terminate.
	Algorithm \ref{alg_inc_train} in Appendix \ref{app_experiments} describes the procedure in detail.
\squishend

For the case of two tasks, we compare the incremental training scheduled described in Algorithm \ref{alg_inc_train}  to a round-robin training schedule baseline.
We add $20\%$ of source task samples for every $T = 2$ epochs.
The total number of epochs is $20$.
We set the threshold $\tau$ as the validation accuracy of the target task using the baseline training schedule.

@@

%We fill in the details of the experimental procedure used for the results in Figure \ref{fig_ablation}.
%\squishlist
%	\item Task similarity: We select a similar and a dissimilar source task compared to the target task using domain knowledge.
%First pair: the customer review dataset (CR) , which predicts whether a review is positive or negative, is more similar to SST (sentiment treebank) than MPQA (question type).
%Second pair: SST is more similar to MR since they both concern about positive or negative opinions expressed the text.
%TREC is less similar to MR because the task is about question types.
%Third pair: MPQA (opinion polarity) is more similar to TREC (question type)

@@

\paragraph{Covariance shift.}
Our observation highlights the need to correct covariate shift when $n_1 / n_2$ is large.
Hence for such settings, we expect procedures that aim at correcting covariate shift to provide more significant gains.
We consider a covariance alignment procedure proposed in \cite{WZR20}, which is designed for the purpose of correcting covariate shift.
The idea is to add an alignment module between the input and the shared module $B$.
This new module is then trained together with $B$ and the output layers.
We validate our insight on this procedure in the experiments.

Covariate shift: We implement the covariance alignment procedure following \cite{WZR20}.
We fix the sample size of the target task as $1000$.

@@

%\textbf{Further results of the covariance alignment procedure.}
%Our results in Figure \ref{fig_ab_cov} are averaged over all the task pairs.
%In Figure \ref{fig_covariate_app}, we show two task pairs as examples.
%In Figure \ref{fig_cov_a}, we observe that for the particular task pair, covariance alignment provides more significant gains when the sample ratio is large.
%In Figure \ref{fig_cov_b}, we observe that covariance alignment does not always improve over the baseline multi-task learning model.
%One explanation is that MR and SST are similar tasks, hence adding the alignment module is unnecessary.
%An interesting question is to understand when adding the alignment module benefits the multi-task learning model.
%We leave this question for future work.
%Note: For text classification tasks, the source task training data size ranges from 500 to 1,500 and target task training data size is 1000; For ChestX-ray14,

%\begin{figure}[!h]
%	\centering
%	\begin{subfigure}[b]{0.48\textwidth}
%		\centering
%		\includegraphics[width=0.7\textwidth]{figures/ratio_alignment_norm_trec_cr_lstm.pdf}
%		\caption{Task pair TREC and CR}
%		\label{fig_cov_a}
%	\end{subfigure}\hfill
%		\begin{subfigure}[b]{0.48\textwidth}
%		\centering
%		\includegraphics[width=0.7\textwidth]{figures/ratio_alignment_mr_sst_lstm.pdf}
%		\caption{Task pair MR and SST}
%			\label{fig_cov_b}
%	\end{subfigure}
%	\caption{(a) For the task pair TREC and CR, adding the covariance alignment procedure provides more improvement when the source/target sample ratio is large.
%	(b) For the task pair MR and SST, adding the covariance alignment procedure hurts performance.
%	One explanation is that MR and SST are similar tasks, hence adding the alignment module is unnecessary.}
%	\label{fig_covariate_app}
%\end{figure}
